Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-06-10 GWLDCII.tex
initial pictures added

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integran associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \]\eas
\end{eg}

@@

\hlfix{[picture]}{is it worth including a picture here?}

@@

>>>>

To calculate $R(W)$, write \bmls R_1 = c_{1,1} c_{1, 2}\quad R_2 = c_{2,2} c_{2,3} \quad R_4 = c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4} \\ R_5 = c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5} \quad R_7 = c_{3,7} c_{3,8} \quad R_8 = c_{4,8} c_{4,1} \;.\emls All other $R_e$ are $1$.  Finally, the integrand associated to this Wilson loop diagram is \bas \Omega(W) = \frac{\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,1}\textrm{d}c_{1,2}\textrm{d}c_{1,4}\textrm{d}c_{1,5}\textrm{d}c_{2,1}\textrm{d}c_{2,3}\textrm{d}c_{2,4}\textrm{d}c_{2,5}\textrm{d}c_{3,5}\textrm{d}c_{3,6}\textrm{d}c_{3,7}\textrm{d}c_{3,7}\textrm{d}c_{4,5}\textrm{d}c_{4,6}\textrm{d}c_{4,8}\textrm{d}c_{4,1}}{c_{1,1} c_{1, 2}c_{2,2} c_{2,3}c_{2,5} (c_{2,4}c_{1,5} - c_{2,5}c_{1,4})c_{1,4}c_{4,6} (c_{4,6}c_{3,5} - c_{3,6}c_{4,5})c_{3,5}c_{3,7} c_{3,8}c_{4,8} c_{4,1}} \;. \eas
\end{eg}

@@

\begin{eg}
Let $W$ be the Wilson loop diagram from Figure \ref{fig:ex of WLD}, reproduced here for convenience.  \[W\ =\ \begin{tikzpicture}[rotate=67.5,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{8}{1.5}
	\drawnumbers
	\drawlabeledprop{1}{0}{4}{0}{\footnotesize $p$}
	\drawprop{2}{0}{4}{-1}
    \drawprop{5}{0}{8}{0}
    \drawprop{5}{1}{7}{0}
		\end{scope}
	\end{tikzpicture}\]

Let $p$ be the propatagor $p = (1, 4)$. Then $\cP_{in}(p, <_4) = \{(1,4), (5, 8), (5, 7) \}$ and $\cP_{out}(p, <_4) = \{(2,4) \}$
\end{eg}

@@

\bas \begin{tikzpicture}[rotate=15,baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLD{20}{1.5}
	%\drawnumbers
	%\drawprop{1}{0}{4}{0}
	\drawlabeledprop{5}{0}{7}{0}{\footnotesize $p_1$}
    \drawlabeledprop{3}{0}{12}{0}{\footnotesize $q_1$}
		\end{scope}
	\end{tikzpicture}\eas
